---
title: "EDUC112"
author: "Nahian Haque"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(sf)
library(ggplot2)
library(dplyr)
```

```{r}
survey <- read.csv("C:/Users/nahia/Downloads/sfusd_survey_4_9_24.csv")
```


```{r}
# Calculate proportions for each unique value in multiple columns
cols <- c("race", "education", "gay", "child_gay", "user_lang", "spec_ed", "ell", "lang_path", "foster", "homeless", "role")

proportions_list <- lapply(survey[cols], function(x) prop.table(table(x)))

# Print the proportions for each column
for (i in 1:length(proportions_list)) {
  cat("Column:", cols[i], "\n")
  print(proportions_list[[i]])
}
```


```{r}
dfs <- list()

for (i in 1:length(proportions_list)) {
  # Create a data frame for the current column
  df <- as.data.frame(proportions_list[[i]])
  # Set appropriate column names
  colnames(df) <- c("category", "proportion")
  # Add the column name as an identifier
  df$column <- cols[i]
  # Append the data frame to the list
  dfs[[i]] <- df
}
```

```{r}
dfs[[1]]
```


```{r}
barplot(height = dfs[[1]]$proportion, names.arg = dfs[[1]]$category, 
        main = paste("Bar plot for", dfs[[1]]$column[1]),
        ylab = "Proportion",
        las = 2, cex.names = 0.5)
text(x = barplot(dfs[[1]]$proportion, add = TRUE),  # Add bars on existing plot and get x-coordinates
     y = dfs[[1]]$proportion,  # Use the same y-coordinates as bars
     labels = scales::percent(dfs[[1]]$proportion),  # Format labels as percentages
     pos = 3, cex = 0.5, col = "black")  # Adjust position, size, and color of text labels
```


Trying geospatial:
```{r}
survey_zips <- as.data.frame(prop.table(table(survey$zip)))
```

```{r}
sf_shp <- st_read("C:/Users/nahia/Downloads/data/sfzipcodes.shp")

sf_zip_merged <- merge(sf_shp, survey_zips,
                       by.x="ZIP_CODE", by.y="Var1", all.x=TRUE, all.y=TRUE)
```

```{r}
ggplot() +
  geom_sf(data = sf_zip_merged,
          aes(fill = Freq), color = "black") +
  scale_fill_gradient(low = "lightblue", high = "darkblue") +
  labs(title = "San Francisco Zip Code Areas by Respondents")
```
Note: There were 107 unique zip codes that did not correspond with a SF zip code (starting with 941)

# Survey Analysis
1. Grouped by race, what are the average responses to each of the Equity, Excellence, Efficiency questions?
2. Same as 1, grouped by zip code
3. Same as 1, grouped by educ.

General Average Responses
```{r}
colMeans(survey[, c(19:34, 40:42)], na.rm = TRUE)
```
Equity
```{r}
survey %>%
  group_by(race) %>%
  summarise_at(vars(eq_his, eq_hin, eq_as, eq_pa, equity),
  list(Mean_Response = mean), na.rm = TRUE)
```
```{r}
survey %>%
  group_by(zip) %>%
  summarise_at(vars(eq_his, eq_hin, eq_as, eq_pa, equity),
  list(Mean_Response = mean), na.rm = TRUE)
```
```{r}
survey %>%
  group_by(education) %>%
  summarise_at(vars(eq_his, eq_hin, eq_as, eq_pa, equity),
  list(Mean_Response = mean), na.rm = TRUE)
```

```{r}
survey %>%
  group_by(role) %>%
  summarise_at(vars(eq_his, eq_hin, eq_as, eq_pa, equity),
  list(Mean_Response = mean), na.rm = TRUE)
```


Excellence
```{r}
survey %>%
  group_by(race) %>%
  summarise_at(vars(ex_ap, ex_scc, ex_sel, ex_sd, ex_att, excellence),
  list(Mean_Response = mean), na.rm = TRUE)
```
```{r}
survey %>%
  group_by(zip) %>%
  summarise_at(vars(ex_ap, ex_scc, ex_sel, ex_sd, ex_att, excellence),
  list(Mean_Response = mean), na.rm = TRUE)
```
```{r}
survey %>%
  group_by(education) %>%
  summarise_at(vars(ex_ap, ex_scc, ex_sel, ex_sd, ex_att, excellence),
  list(Mean_Response = mean), na.rm = TRUE)
```

```{r}
survey %>%
  group_by(role) %>%
  summarise_at(vars(ex_ap, ex_scc, ex_sel, ex_sd, ex_att, excellence),
  list(Mean_Response = mean), na.rm = TRUE)
```



Efficiency 
```{r}
survey %>%
  group_by(race) %>%
  summarise_at(vars(er_se, er_fc, er_bu, er_bc, er_cpp, er_ocs, er_tt, efficiency),
  list(Mean_Response = mean), na.rm = TRUE)
```

```{r}
survey %>%
  group_by(zip) %>%
  summarise_at(vars(er_se, er_fc, er_bu, er_bc, er_cpp, er_ocs, er_tt, efficiency),
  list(Mean_Response = mean), na.rm = TRUE)
```

```{r}
survey %>%
  group_by(education) %>%
  summarise_at(vars(er_se, er_fc, er_bu, er_bc, er_cpp, er_ocs, er_tt, efficiency),
  list(Mean_Response = mean), na.rm = TRUE)
```

```{r}
survey %>%
  group_by(role) %>%
  summarise_at(vars(er_se, er_fc, er_bu, er_bc, er_cpp, er_ocs, er_tt, efficiency),
  list(Mean_Response = mean), na.rm = TRUE)
```


#Format the written answers
```{r}
unique_equity_sugg <- distinct(survey, equity_sugg)
```



